\chapter{Introduction}
With rapid advances in the field of machine learning, we are discovering a myriad of innovative applications of the technology. In particular, agriculture is a field that machine learning is beginning to revolutionize. Our motivations for improving agriculture are clear: feeding more people, utilizing fewer resources, and reducing the need for physical labor.

This work aims to utilize data collected from sensors to analyze the health of various crops. Particularly, we are interested in utilizing sensors mounted on unmanned aerial vehicles (UAVs) to collect data. This is due to the speed at which these systems can collect data and the accessibility for our end users. Given this data, we leverage convolutional neural networks (CNNs) to make predictions about the crops to determine whether there is an adequate amount of water and fertilizer. This system will enable farmers to target the specific plants that require water or fertilizer treatments, thus conserving resources. Applications of our technology will also improve overall crop health, which reduces unnecessary plant waste.

Our work focuses on two crops specifically: lettuce and oranges. California is the largest producer of lettuce in the U.S. with 73\% of total lettuce acreage \cite{Lettuce}. Moreover, over 30\% of U.S. orange production comes from California \cite{Orange}. Since these crops are clearly significant to the California agriculture industry, our work will have the largest impact as such.